\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{gdalunes} Gabriele D'Angelo, Stefano Ferretti
{\em Highly intensive data dissemination in complex networks},
Journal of Parallel and Distributed Computing, Elsevier, vol. 99, 2017

\bibitem{bitcoinwhite} Satoshi Nakamoto
{\em Bitcoin: A Peer-to-Peer Electronic Cash System},
\url{https://bitcoin.org/bitcoin.pdf}, 31 October 2008

\bibitem{bizantine} Leslie Lamport, Robert Shostak, Marshall Pease
{\em The Byzantine Generals Problem}
ACM Transactions on Programming Languages and Systems, Vol. 4, No. 3, pp. 382-401., 3 July 1982

\bibitem{ethereumwhite} Vitalik Buterin
{\em A next generation smart contract and decentralized application},
\url{https://github.com/ethereum/wiki/wiki/White-Paper}, 2013

\bibitem Vitalik Buterin
{\em Visions, Part 1: The Value of Blockchain Technology}
\url{https://blog.ethereum.org}, 2015

\bibitem{chaum} David Chaum
{\em Security without identification: transaction systems to make big brother obsolete},
Communications of the ACM, Vol. 28, No. 10, pp. 1030-1044, 1985

\bibitem{bitcoin} Arvind Narayanan, Joseph Bonneau, Edward Felten, Andrew Miller, Steven Goldfeder
{\em Bitcoin and Cryptocurrency Technologies},
Princeton University Press, 2016

\bibitem{haberstornetta} Stuart Haber, W. Scott Stornetta
{\em How to Time-Stamp a Digital Document},
Journal of Cryptology, Vol. 3, No. 2, pp. 99-111, 1991

\bibitem{cypherpunk} Eric Hughes
{\em A Cypherpunk's Manifesto},
9 March 1993

\bibitem{owning} Richard L. Apodaca
{\em Owning Bitcoin, the illustrate guide to security, privacy and possibility},
Bitzuma, 2017

\bibitem{ecdsa} Johnson, Don and Menezes, Alfred and Vanstone, Scott
{\em TheEllipticCurveDigitalSignatureAlgorithm(ECDSA)},
International Journal of Information Security, pp 36-63, 2001

\bibitem{elliptic} Joppe W. BosJ. Alex Halderman, Nadia Heninger, Jonathan Moore, Michael Naehrig, Eric Wustrow
{\em Elliptic Curve Cryptography in Practice}
Christin, Nicolas and Safavi-Naini, Reihaneh, Financial Cryptography and Data Security, pp. 157-175, 2014

\bibitem{ethereum} Chris Dannen
{\em Introducing Ehtereum and solidity},
Apress, 2017.

\bibitem{bitcoinsimulator} Gervais, Arthur and Karame, Ghassan and Wüst, Karl and Glykantzis, Vasileios and Ritzdorf, Hubert and Capkun, Srdjan
{\em On the Security and Performance of Proof of Work Blockchains},
Proceedings of the 23nd ACM SIGSAC Conference on Computer and Communication Security (CCS), 2016

\bibitem{networksize} Muntadher Fadhil, Gareth Owen, Mo Adda
{\em Bitcoin Network Measurements for Simulation Validation and Parameterisation},
Conference: INC 2016, 2016

\bibitem{limitbitcoin} Eric Budish
{\em The Economic Limits of Bitcoin and the Blockchain}
NBER Working Paper No. 24717, Issued in June 2018, 2018

\bibitem{crytogeneric} Patrick Wilder
{\em Cryptocurrency Masterclass},
Patrick Wilder, 2018

\bibitem{antonio} Antonio Magnani
{\em Design, implementation and performance evaluation of an anonymous distributed simulator},
Alma Mater Studiorum Università di Bologna, 2015

\bibitem{artis} Gabriele D'Angelo, Moreno Marzolla
{\em New trends in parallel and distributed simulation: From many-cores to cloud computing},
Simulation Modelling Practice and Theory, 49:320–335, 2014

\bibitem{gossip} Gabriele D'Angelo, Stefano Ferretti, Moreno Marzolla
{\em Adaptive Event Dissemination for Peer-to-Peer Multiplayer Online Game},
Proceedings of 2nd ICST/CREATE-NET Workshopon DIstributed SImulation and Online gaming (DISIO 2011).
In conjunction with SIMUTools 2011. Barcelona, Spain, March 2011. ISBN 978-1-936968-00-8

\bibitem{coinhop} Dmitry Meshkov, Alexander Chepurnoy, Marc Jansen
{\em Revisiting Difficulty Control for Blockchain System},
University of Applied Sciences Ruhr West

\bibitem{btcsecurity} Mauro Conti, S. K. E, C. Lal, S. Ruj
{\em A Survey on Security and Privacy Issues of Bitcoin}, 
IEEE Communications Surveys Tutorials, pp. 1-1, 2018

\bibitem{selfish} Ittay Eyal, Emin Gun Sirer
{\em Majority is not Enough: Bitcoin Mining is Vulnerable},
CoRR, abs/1311.0243, 2013

\bibitem{mtgox} Christian Decker, Roger Wattenhofer
{\em Bitcoin Transaction Malleability and MtGox},
Kuty{\l}owski, Miros{\l}aw and Vaidya, Jaideep, Computer Security - ESORICS, pp. 313-326, 2014

\bibitem{selfish} Sapirshtein, Ayelet and Sompolinsky, Yonatan and Zohar, Aviv
{\em Optimal Selfish Mining Strategies in Bitcoin},
Financial Cryptography and Data Security, Springer Berlin Heidelberg, pp. 515-532, 2017

\bibitem{selfishvitalik} Vitalik Buterin
{\em Selfish Mining: A 25\% Attack Against the Bitcoin Network}
\url{bitcoinmagazine.com}, 2013

\bibitem{51\%} Bruce Feynman
{\em How Profitable it is to do a 51\% attack — a very simple step by step calculation}
\url{https://hackernoon.com/}, 2018

\bibitem{padssite} Parallel and Distributed Simulation Research Group
{\em \url{http://pads.cs.unibo.it/doku.php?id=pads:gaia-apis}}

\bibitem{bitcoinwiki} Bitcoin Wiki
{\em \url{https://en.bitcoin.it/wiki/Main_Page}}

\bibitem{coindesk} CoinDesk News
{\em \url{https://www.coindesk.com/}}

\bibitem{bitnodes} Bitnodes
{\em \url{https://bitnodes.earn.com/}}

\bibitem{bitnodesgh} Bitnodes Repository
{\em \url{https://github.com/ayeowch/bitnodes}}

\end{thebibliography}

% NeoTex: mainfile=main.tex:
